\thetitle

### 2020-11-21 writing/introduction.tex
Minor rewordings in intro and challenges

The paper's second contribution is a set of results from applying the evaluation
method to three distinct blame assignment strategies and approximately
722,000 cases (section~\ref{sec:results}): Vitousek et
al.'s strategy of tracking typed/untyped boundaries in Reticulated;
Tobin-Hochstadt et al.'s use of higher-order contract system~\cite{ff-icfp-2002,
mf-toplas-2009}; and the approach of industrial systems that forego blame
and instead rely on error messages from the
underlying programming language. A direct interpretation of the results
(section~\ref{sec:discussion}) is that
they validate the conjecture behind the work of theoreticians. A good blame assignment
strategy helps the search for impedance mismatches between the specified types
and the behavior of untyped components. Even better, the evaluation method 
identifies the wrapper-based blame tracking of Typed Racket as the most
useful academic system with that of Reticulated Python only marginally  behind.

Next, the paper describes the challenges of developing an evaluation
method, which may explain why the question has been neglected for such
a long time.

>>>>

The paper's second contribution is a set of results from applying the evaluation
method to three distinct blame assignment strategies and approximately
722,000 cases (section~\ref{sec:results}): Vitousek et
al.'s strategy of tracking typed/untyped boundaries in Reticulated, called Transient;
Tobin-Hochstadt et al.'s use of higher-order contract system~\cite{ff-icfp-2002,
mf-toplas-2009}, called Natural; and the approach of industrial systems that forego blame
and instead rely on error messages from the
underlying programming language, called Erasure. A direct interpretation of the results
(section~\ref{sec:discussion}) is that
they validate the conjecture behind the work of theoreticians. A good blame assignment
strategy helps the search for impedance mismatches between the specified types
and the behavior of untyped components.
Furthermore, the evaluation method
identifies the wrapper-based blame tracking of Typed Racket as the most
useful approach, with that of Reticulated Python close behind.

Next, the paper describes the challenges of developing an evaluation
method for blame, which may explain why the question has been neglected for such
a long time.
